\textbf{Emergency Service Location Optimization in a Multi-Zone District based on Population Distribution}

### 2013-11-16 LaTeX/paper.tex
Fixing detached head

\section{Assumptions and Justifications}
\begin{enumerate}
    \item
        The travel times given are calculated from an optimal route from the center of the first
        zone to the center of ths econd. This excludes the possibility of reaching a zone faster
        via an indirect route from the direct, given one.
    \item
        The travel times given for travel from any zone to itself is the average
        of all the travel times of the different routes within that zone.
    \item
        The ratio between the time it takes inside a zone to travel toward a second zone,
        to the time it takes inside a zone to return from a second, is equal to the ratio
        between the travel time from the first zone to the second, and the travel time from the
        second to the first.
    \item
        Ambulances can only be placed in the very center of a zone. Because we do not know the
        spacial position of the zones relative to each other, we cannot consider the ambulances
        being closer to one zone or another.
    \item
        Partial ambulance coverage of a zone will be treated as incomplete even coverage over the entire
        zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, we assume
        that multiple ambulances will cover different areas of the zones, thus evening out coverage.
        (If partial coverages from multiple ambulances sum to above the total population of a zone,
        we assume that zone is completely covered by the ambulances.)
\end{enumerate}

>>>>

\section{Assumptions and Justifications}
\begin{description}
    \item[1. Zone to Zone Travel] \hfill \\
    	The travel times given are calculated from an optimal route from the center of the first
        zone to the center of the second. This excludes the possibility of reaching a zone faster
        via an indirect route from the direct, given one.
    \item[2. Zone Interior Travel] \hfill \\
    	The travel times given for travel from any zone to itself is the average
        of all the travel times of the different routes within that zone.
    \item[3. Zone Directional Travel] \hfill \\
    	The ratio between the time it takes inside a zone to travel toward a second zone,
        to the time it takes inside a zone to return from a second, is equal to the ratio
        between the travel time from the first zone to the second, and the travel time from the
        second to the first.
    \item[4. Ambulance Placement] \hfill \\
        Ambulances can only be placed in the very center of a zone. Because we do not know the
        spacial position of the zones relative to each other, we cannot consider the ambulances
        being closer to one zone or another.
    \item[5. Partial Coverage] \hfill \\
        Partial ambulance coverage of a zone will be treated as imcomplete even coverage over the entire
        zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, we assume
        that multiple ambulances will cover different areas of the zones, thus evening out coverage. (If partial coverages from multiple ambulances sum to above the total population of a zone,
        we assume that zone is completely covered by the ambulances.)
\end{description}
